Usage metrics

### 2021-01-02 analysis/usage.Rmd
direct_interpreter_eval -> interp_eval

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/
  calls_path: base/summarized.fst
  corpus_path: corpus.fst
  static_path: package-evals-static.csv
  force_rebuild: TRUE
---

@@

  if (!"direct_interpreter_eval" %in% names(E_raw)) { # We are dealing with
    E_raw %>% mutate(direct_interpreter_eval=0) -> E_raw # partial data.
  } #                                                  We create a fake column.

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    arg_size = expr_resolved_length, #   Size in characters of argument 
    ast_nodes = expr_resolved_nodes, #   Size in AST Nodes
    type = expr_resolved_type_tag,   #   Argument type
    opcodes = direct_interpreter_eval #  Count of the AST nodes traversed by the
  ) %>% #                                interpreter during eval (non-recursive).
   mutate(across(where(is_character),as_factor)) -> E 
  write.fst(E, "Data/E.fst")
  sz <- file.size(calls_path) %>% as_tibble()
  write.fst(sz,"Data/.lock.fst")
}

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  corpus_path: ../corpus.fst
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    arg_size = expr_resolved_length, #   Size in characters of argument 
    ast_nodes = expr_resolved_nodes, #   Size in AST Nodes
    type = expr_resolved_type_tag,   #   Argument type
    opcodes = interp_eval #  Count of the AST nodes traversed by the
  ) %>% #                                interpreter during eval (non-recursive).
   mutate(across(where(is_character),as_factor)) -> E 
  write.fst(E, "Data/E.fst")
  sz <- file.size(calls_path) %>% as_tibble()
  write.fst(sz,"Data/.lock.fst")
}
